Reply to: 2022-05603 Intentional release of native species undermines ecological stability

### 2022-10-19 rmd/reply_r1.Rmd
reply

*Is the subject sufficiently general? Hatchery supplementation of salmonid populations is common practice globally. However, are there other taxa where this issue pertains? Though the authors a couple of citations, I worry this system may be a bit niche for readers of PNAS. I recommend the authors describe specific case studies in the Discussion where similar dynamics may apply and point to the types of additional research needed to determine if similar inferences may apply in those systems. Also, it would be helpful to include (widely available) estimates of the extent of salmonid hatchery supplementation in North America, and to contextualize the dynamics estimated in the state space model for masu salmon relative to these other well-studied populations.*

@@

> Thank you - we have given a deep thought on this. Masu salmon has a 1-year marine life stage (typically). However, many other species are also diadromous, and some of them return freshwater in a couple of months (e.g., amphidromous). Given the complexity of this system, we reconsidered our state-space model to account for up to AR3 process (fish species in our system typically 1-3 years of life-span). The results were qualitatively similar.

@@

> We agree that our results are not surprising -- we are not surprised either. However, we strongly believe that our result is important and worth publishing because to our knowledge, no study has rigorously quantified the community-level impact of intentional release in the long-term. Also, and perhaps more importantly, many release programs for commercial and recreational species release **millions of individuals to a single system EVERY YEAR** (clarified in the revised manuscript)! This magnitude is way larger than the release program in our study system. Therefore, release numbers of $5\times$ carrying capacity seem even conservative to us. Although we cannot provide quantitative evidence for this claim (we found no data on the carrying capacities of the recipient ecosystems), our analysis should represent a conservative scenario, rather than an extreme, unrealistic scenario.
>
> Regarding the competition coefficient, please note that the interspecific competition coefficients $\alpha_{ij}$ ($i \ne j$) are measured relative to intraspecific competition, i.e., two competing species can coexist when $\alpha_{ij} < 1$ (if carrying capacities are identical between the species). The values in our simulation (0.25 or 0.50 in the revised manusucript) are thus weak enough to allow species co-existence in the absence of intentional release. Therefore, it is certain that the intentional release disrupted the sensitive balance of species interactions. In the revised text, we have also provided empirical estimates of species interactions -- the median value was 0.29, so our simulation setup is reasonable.

*But in the mean* $\mu$ *panel in Figure 1A, the enhanced population shows no effect of releases until about 2x carrying capacity, which seems significant. This appears to occur at the same time there is steep decline of the unenhanced species, even when the number of releases is below.*

@@

> Thank you, we agree that a detailed life-history model will provide useful insights into salmon management. However, we decided not to perform this analysis for the following reasons. First, given the readership of PNAS, as well as the suggestions from reviewer 1 and editor, we believe it is important to keep our model as general as possible. In fact, as clarified in the revised manuscript, there are a number of cases where our phenomenological model may apply. Second, a detailed life-history model has already been developed by Morita et al. [@moritaTemperaturedependentVariationAlternative2014]. The readers interested in specifics of masu salmon can refer to this article. We have cited it in the revised manuscript. Lastly, we believe the reviewer has misread our results in the previous manuscript. Table S9 in the previous manuscript did not show significant effects of ocean productivity (coef = $0.09 \pm 0.29$) or forest cover (coef = $0.36 \pm 0.28$), thus largely overlapping zero or marginal at best. This result remains the same in the improved analysis in the revised manuscript. Therefore, there is little evidence supporting the importance of detailed life-history processes in explaining long-term population dynamics for our dataset.

@@

> We are glad that the reviewer caught this issue. We improved as follows:
>
> \- enriched the text explaining masu salmon's life history
>
> \- added species traits to Table S2
>
> \- added spatial/temporal overlap between masu salmon and other species (see Table S16 for co-occurrence matrix)
>
> As we clarified in the revised text, we are pretty sure that (hatchery) masu salmon interact with other species. Indeed, masu salmon always occurred with other species (in particular, white-spotted charr, sculpins, stone loaches). In addition, there are numerous research documenting competition between masu salmon and other stream fish species. We have clarified these points in the revised manuscript.

@@

> Thank you, this is very important. To address this issue, we have developed a Bayesian Ricker model to estimate competition coefficients in our data (note: we used a subset of data because it requires non-sparse data to estimate parameters reliably). The results were very promising, supporting the considerable interspecific competition among stream fishes. We chose this approach to make it directly comparable with theoretical parameters. As the reviewer suggests, spatial/diet overlap may be useful, but it does not necessarily translate into "population" level interactions (in fact, estimated competition coefficients are varied greatly among sites for a given species pair). Therefore, our approach would give stronger evidence for interspecific competition occurring in natural systems.

@@

>>>>

*Is the subject sufficiently general? Hatchery supplementation of salmonid populations is common practice globally. However, are there other taxa where this issue pertains? Though the authors a couple of citations, I worry this system may be a bit niche for readers of PNAS. I recommend the authors describe specific case studies in the Discussion where similar dynamics may apply and point to the types of additional research needed to determine if similar inferences may apply in those systems.*

*Also, it would be helpful to include (widely available) estimates of the extent of salmonid hatchery supplementation in North America, and to contextualize the dynamics estimated in the state space model for masu salmon relative to these other well-studied populations.*

@@

> Thank you - we have given a deep thought on this. Masu salmon has a 1-year marine life stage. However, many other species are also diadromous, and some of them return freshwater in a couple of months (e.g., amphidromous). Given the complexity of this system, we reconsidered our state-space model to account for up to AR3 process (fish species in our system typically 1-3 years of life-span; see Methods for the revised model). The results were qualitatively similar.

@@

> We agree that our results are not surprising -- we are not surprised either. However, we strongly believe that our result is important and worth publishing because to our knowledge, no study has rigorously quantified the community-level impact of intentional release in the long-term. Also, and perhaps more importantly, many release programs for commercial and recreational species release **millions of individuals to a single system every year** (clarified in the revised manuscript)! This magnitude is way larger than the release program in our study system. Therefore, release numbers of $5\times$ carrying capacity seem even conservative to us. Although we cannot provide quantitative evidence for this claim (we found no data on the carrying capacities of the recipient ecosystems), our analysis should represent a conservative scenario, rather than an unrealistic extreme scenario.
>
> Regarding the competition coefficient, please find that the interspecific competition coefficients $\alpha_{ij}$ ($i \ne j$) are measured relative to intraspecific competition -- i.e., two competing species can coexist when $\alpha_{ij} < 1$ (if carrying capacities are identical between the species). The values in our simulation (0.25 or 0.50 in the revised manuscript) are thus weak enough to allow species co-existence in the absence of intentional release. Therefore, it is certain that the intentional release disrupted the sensitive balance of species interactions. In the revised text, we have also provided empirical estimates of species interactions -- the median value was 0.29, so our simulation setup is reasonable.

*...in the mean* $\mu$ *panel in Figure 1A, the enhanced population shows no effect of releases until about 2x carrying capacity, which seems significant. This appears to occur at the same time there is steep decline of the unenhanced species, even when the number of releases is below.*

@@

> Thank you, we agree that a detailed life-history model will provide useful insights into salmon management. However, we decided not to perform this analysis for the following reasons. First, given the readership of PNAS, as well as the suggestions from reviewer 1 and editor, we believe it is important to keep our model as general as possible. In fact, as clarified in the revised manuscript, there are a number of cases where our phenomenological model may apply. Second, a detailed life-history model has already been developed by Morita et al. [@moritaTemperaturedependentVariationAlternative2014]. The readers interested in specifics of masu salmon can refer to this article. We have cited it in the revised manuscript. Lastly, we believe the reviewer misread our results in the previous manuscript. Table S9 in the previous manuscript did not show significant effects of ocean productivity (coef = $0.09 \pm 0.29$) or forest cover (coef = $0.36 \pm 0.28$), thus largely overlapping zero or marginal at best. This result remains the same in the improved analysis in the revised manuscript. Therefore, there is little evidence supporting the importance of detailed life-history processes in explaining long-term population dynamics for our dataset.

@@

> We are glad that the reviewer caught this issue. We improved as follows:
>
> \- Enriched the text explaining masu salmon's life history; they spend at least one year in freshwater.
>
> \- Added species traits to Table S2.
>
> \- Added spatial/temporal overlap between masu salmon and other species (see Table S16 for co-occurrence matrix).
>
> As we clarified in the revised text, we are pretty sure that (hatchery) masu salmon interact with other species. Indeed, masu salmon always occurred with other species (in particular, white-spotted charr, sculpins, stone loaches). In addition, there are numerous research documenting competition between masu salmon and other stream fish species. We have clarified these points in the revised manuscript.

@@

> Thank you, this is very important. To address this issue, we have developed a Bayesian Ricker model to estimate competition coefficients in our data (note: we used a subset of data because it requires non-sparse data to estimate parameters reliably). The results were very promising, supporting the considerable interspecific competition among stream fishes. We chose this approach to make it directly comparable with theoretical parameters. As the reviewer suggests, spatial/diet overlap may be useful, but it does not necessarily translate into "population" level interactions (in fact, estimated competition coefficients varied greatly among sites for a given species pair). Therefore, our approach would give stronger evidence for interspecific competition occurring in natural systems.

@@

> We appreciate the careful reading by the reviewer. We agree, and we have substantially improved the introduction and discussion to address this issue. Specifically, we now recognized that there are a number of cases where stock enhancement is economically successful -- we have mentioned these examples to properly develop a context. Also, where applicable, we have softened the language throughout the manuscript. If there are information/issues that we have missed, please let us know and we will address them too. This insightful comment helped a lot to avoid delivering wrong messages.
